The Name of the Title is Hope

### 2019-04-04 emsoft-2019/Motiv.tex

	\tikzstyle{block} = [draw, fill=blue!20, rectangle, 
	minimum height=3em, minimum width=6em]
	\tikzstyle{sum} = [draw, fill=blue!20, circle, node distance=1cm]
	\tikzstyle{input} = [coordinate]
	\tikzstyle{output} = [coordinate]
	\tikzstyle{pinstyle} = [pin edge={to-,thin,black}]
	\begin{figure*}[t]
		\begin{tikzpicture}[auto, node distance=2cm,>=latex',scale=1]
			\centering
			\node [block, pin={[pinstyle]above:$\delta=\delta_0$},
			node distance=5cm] (RMPC) {Robust MPC design};
			\node[] (partitions) at (2.5,.5){\includegraphics[width=.08\textwidth]{Figs/regs.jpg}};
			\node [block, right of=RMPC,
			node distance=5cm,text width=3cm] (mixed) {Mixed precision analysis};
			\node [draw, fill=blue!20, diamond, 
			minimum height=3em, minimum width=3em, right of=mixed,
			node distance=5cm] (decide) {Is memory violated?};
			\node [block, right of=decide,
			node distance=3cm] (done) {Done};
			\node [block, below of= decide,
			node distance=3cm] (delta) {increase $\delta$};

>>>>

	\tikzstyle{block} = [draw, fill=blue!20, rectangle, 
	minimum height=3em, minimum width=6em]
	\tikzstyle{sum} = [draw, fill=blue!20, circle, node distance=1cm]
	\tikzstyle{input} = [coordinate]
	\tikzstyle{output} = [coordinate]
	\tikzstyle{pinstyle} = [pin edge={to-,thin,black}]
	\begin{figure*}[t]
		\begin{tikzpicture}[auto, node distance=2cm,>=latex',scale=1]
			\centering
			\node [block, pin={[pinstyle]above:$\Delta=\Delta_0$},
			node distance=5cm] (RMPC) {Robust MPC design};
			\node[] (partitions) at (2.5,.5){\includegraphics[width=.08\textwidth]{Figs/regs.jpg}};
			\node [block, right of=RMPC,
			node distance=5cm,text width=3cm] (mixed) {Mixed precision analysis};
			\node [draw, fill=blue!20, diamond, 
			minimum height=3em, minimum width=3em, right of=mixed,
			node distance=5cm] (decide) {Is memory violated?};
			\node [block, right of=decide,
			node distance=3cm] (done) {Done};
			\node [block, below of= decide,
			node distance=3cm] (delta) {increase $\Delta$};
